Learning \strips\ action models from {\em state-invariants}

### 2019-02-06 doc/ijcai-19-deductivelearning/deductivelearning.tex
complete version for sections 1,2 and 3 ijcai19 paper on deductive learning

\begin{abstract}
This paper addresses the learning of action models from {\em deductive} knowledge with the form of {\em state-invariants} (i.e logic formulae that specify constraints about the possible states of a given domain) to reduce the negative effects of insufficient input observations. Given an action model, state-of-the-art planners use it to infer {\em state-invariants} that reduce the planner search space and make the planning process more efficient~\cite{helmert2009concise}. In this paper we follow the opposite direction and exploit {\em state-invariants} to learn a planning action model.
\end{abstract}

@@

The specification of planning action models is a complex process that limits, too often, the application of {\em model-based planning} to real-world tasks~\cite{kambhampati:modellite:AAAI2007}. The {\em machine learning} of action models can relieve the {\em knowledge acquisition bottleneck} of planning and nowadays, there exists a wide range of effective approaches for learning action models~\cite{arora:amodels:ker2018}. Many of the most successful approaches for learning planning action models are however purely {\em inductive}~\cite{yang2007learning,pasula2007learning,mourao2010learning,zhuo2013action}, meaning that their performance depends on the {\em amount} and {\em quality} of the input examples (namely observations of plan executions generated by the aimed action model).

This paper addresses the learning of action models from {\em deductive} knowledge with the form of {\em state-invariants} (i.e logic formulae that specify constraints about the possible states of a given domain) to reduce the negative effects of insufficient input observations. Given an action model, state-of-the-art planners use it to infer {\em state-invariants} that reduce the planner search space and make the planning process more efficient~\cite{helmert2009concise}. In this paper we follow the opposite direction and exploit {\em state-invariants} to learn a planning action model.

Our approach is built on top of the {\em classical planning} compilation for the learning of \strips\ action models~\cite{aineto2018learning}. This compilation is flexible to different kinds of input knowledge (e.g., partially/fully observations of actions of plan executions as well as partially/fully observed intermediate states) and outputs an action model that is {\em consistent} with the given input knowledge. In this paper we show that, in unfavorable scenarios where input observations are minimal (just an {\em initial state} and the {\em goals}), {\em state-invariant} help to learn better \strips\ models with the {\em classical planning} compilation.

@@

\subsection{State-invaraints}
The notion of {\em state-constraint} is very general and has been used in different areas of AI and for different purposes.  If we restrict ourselves to planning, {\em state-constraints} are abstractions for compactly specifying sets of states. For instance, {\em state-constraints} in planning allow to specify the set of states where a given action is applicable, the set of states where a given {\em derived predicate} holds or the set of states that are considered goal states.

@@

\section{Learning \strips\ action models from {\em state-invaraints}}
\label{sec:learning}

We define the task of learning an action model from {\em state-invaraints} as a tuple $\Lambda=\tup{P,\Phi,M}$, where:
\begin{itemize}
\item $P=\tup{F,A[\cdot],I,G}$, is a {\em classical planning problem} where $A[\cdot]$ is a set of actions s.t., the semantics of each action $a\in A[\cdot]$ is unknown (i.e. the functions $\rho$ and/or $\theta$ of $a$ are undefined).
\item $\Phi$, a set of {\em state-invariants} that constrain the set of possible states in the given domain.
\item $M$ is the {\em space of possible action model} for the $A[\cdot]$ actions. This set is the {\em full} space of action models, when learning from scratch, or a {\em partially specified action model}, when some fragments of the aimed action model are a priori known. A set of action models can be defined {\em explicitly}, enumerating all the models that belong to the set or {\em implicitly}, enumerating all the constraints that must satisfy any model that belongs to the set. A {\em partially specified} \strips\ action model is then a formalism for the {\em implicit} representation of a set of \strips\ schemes~\cite{sreedharan2018handling}.
\end{itemize}

A {\em solution} to a $\Lambda=\tup{P,\Phi,M}$ learning task is a model $\mathcal{M}'\in M$ such that there exists a plan $\pi$ satisfying that any state traversed in the trajectory $\tau(\pi,P)$ satisfies all the {\em state-invariants} in $\Phi$. Inductive approaches for the learning planning action models compute an action model that maximizes some notion of {\em statistical consistency} over a set of observations of plan executions so output an action model in our case a solution to the addressed learning task is an action model that is {\em consistent} with the input knowledge.

@@

Despite any element of ${\mathcal I}_{\Psi,\xi}$ can {\em a priori} appear in the $pre(\xi)$, $del(\xi)$ and $add(\xi)$ of schema $\xi$, the actual space of possible \strips\ schemata is bounded by constraints of three kinds:
\begin{enumerate}
\item {\bf Syntactic constraints}. \strips\ constraints require $del(\xi)\subseteq pre(\xi)$, $del(\xi)\cap add(\xi)=\emptyset$ and $pre(\xi)\cap add(\xi)=\emptyset$. Considering exclusively these syntactic constraints, the size of the space of possible \strips\ schemata is given by $2^{2\times|{\mathcal I}_{\Psi,\xi}|}$. {\em Typing constraints} are also of this kind~\cite{mcdermott1998pddl}. 
\item {\bf Domain-specific constraints}. One can introduce domain-specific knowledge to constrain further the space of possible schemata. For instance, in the {\em blocksworld} one can argue that {\small\tt on($v_1$,$v_1$)} and {\small\tt on($v_2$,$v_2$)} will not appear in the $pre(\xi)$, $del(\xi)$ and $add(\xi)$ lists of an action schema $\xi$ because, in this specific domain, a block cannot be on top of itself. {\it State invariants} are also constraints of this kind. 
\item {\bf Observation constraints}. An observation $\mathcal{O}(\tau)$ depicts {\em semantic knowledge} that constraints further the space of possible action schemata.   
\end{enumerate}

@@

\subsection{Learning \strips\ action models with classical planning}
Given a $\Lambda=\tup{P,\Phi,M}$ where $\Phi$ is a set of {\em domain mutex} $\phi\in\Phi$, we create a classical planning problem $P'=\tup{F',A',I,G}$ such that:
\begin{itemize}
\item $F'$ extends $F$ with a fluent ${\tt inconsistent}$, to indicate whether an action model is {\em inconsistent} with the input {\em state-invariants}, a fluent $mode_{insert}$, to indicate whether action models are being programmed, and the fluents for the propositional encoding of the corresponding space of STRIPS action models. This is a set of fluents of the type $\{pre\_e\_\xi, eff\_e\_\xi\}_{\forall e\in{\mathcal I}_{\Psi,\xi}}$ such that $e\in{\mathcal I}_{\Psi,\xi}$ is a single element from the set of FOL interpretations of predicates $\Psi$ over the corresponding action parameters $pars(\xi)$.

\item $A'$ replaces the actions in $A$ with two types of actions.
\begin{enumerate}
\item Actions for {\em inserting} a {\em precondition}, {\em positive} effect or {\em negative} effect in $\xi$ following the syntactic constraints of \strips\ models. In the particular case that $M$ is a {\em partially specified model} then only the actions for inserting a possible {\em precondition} or {\em effect} are necessary.
\begin{itemize}
\item Actions which support the addition of a {\em precondition} $p\in \Psi_{\xi}$ to the action model $\xi$. A precondition $p$ is inserted in $\xi$ when neither $pre_p$, $eff_p$ exist in $\xi$.

@@

\item Actions for {\em applying} an action model $\xi$ built by the {\em insert} actions and bounded to objects $\omega\subseteq\Omega^{|pars(\xi)|}$ (where $\Omega$ is the set of {\em objects} used to induce the fluents $F$ by assigning objects in $\Omega$ to the $\Psi$ predicates and $\Omega^k$ is the $k$-th Cartesian power of $\Omega$). The action parameters, $pars(\xi)$, are bound to the objects in $\omega$ that appear in the same position.
\end{enumerate}
\end{itemize}

\begin{small}
\begin{align*}
\pre(\mathsf{apply_{\xi,\omega}})=&\{\emptyset\},\\
\cond(\mathsf{apply_{\xi,\omega}})=&\{pre_{p}(\xi)\wedge \neg p(\omega)\}_{\forall p\in\Psi_\xi},\\
&\{pre_{p}(\xi)\wedge eff_{p}(\xi)\}\rhd\{\neg p(\omega)\}_{\forall p\in\Psi_\xi},\\
&\{\neg pre_{p}(\xi)\wedge eff_{p}(\xi)\}\rhd\{p(\omega)\}_{\forall p\in\Psi\xi}\},\\
&\{\emptyset\}\rhd\{\neg mode_{insert}\}.
\end{align*}
\end{small}

\section{Learning from {\em state-invariants} and observations of plan executions}
\label{sec:observations}
Most of the approachs for leanning planning action mdoels compute an action model that maximizes some notion of {\em statistical consistency} over a set of observations of plan executions so output an action model that is {\em consistent} with the input knowledge.

@@

\subsection{Extending the compilation to deal with {\em plan recognition as planning}}
The work on {\em plan recognition as planning} usually assumes an observation model that is referred only to logs of executed actions. However, the approach applies also to more expressive observation models that consider state observations as well, like the observation model defined above, with a simple three-fold extension:
\begin{itemize}
\item One fluent $\{validated_j\}_{0\leq j\leq m}$ to point at every $s_j^o\in\mathcal{O}(\tau)$ state observation. Two fluents, $at_i$ and $next_{i,i+1}$, {\small $1\leq i \leq n$}, to iterate through the $n$ observed actions of $\tau$. The former is used to ensure that actions are executed in the same order as they are observed in $\tau$. The latter is used to iterate to the next planning step when solving $P_{\Lambda}$.
\item Adding $at_1$ and $\{next_{i,i+1}\}$, {\small $1\leq i \leq n$} to the initial state and $validated_m$ to every possible goal $G\in G[\cdot]$ to constrain solution plans $\pi^\top$ to be consistent with all the state observations.

>>>>

\begin{abstract}
This paper addresses the learning of action models from {\em state-invariants} (i.e logic formulae that specify constraints about the possible states of a given domain) to reduce the negative effects of insufficient learning examples. Our approach is built on top of a {\em classical planning} compilation that is flexible to different kinds of input knowledge (e.g., partially/fully observations of actions of plan executions as well as partially/fully observed intermediate states) and outputs an action model that is {\em consistent} with the given input knowledge. The experimental results show that, at unfavorable scenarios where input observations are minimal (just an {\em initial state} and the {\em goals}), {\em state-invariant} are helpful to learn better \strips\ action models.
\end{abstract}

@@

The specification of planning action models is a complex process that limits, too often, the application of {\em model-based planning} systems to real-world tasks~\cite{kambhampati:modellite:AAAI2007}. The {\em machine learning} of action models can relieve the {\em knowledge acquisition bottleneck} of planning and nowadays, there exists a wide range of effective approaches for learning action models~\cite{arora:amodels:ker2018}. Many of the most successful approaches for learning planning action models are however purely {\em inductive}~\cite{yang2007learning,pasula2007learning,mourao2010learning,zhuo2013action}, meaning that their performance is linked to the {\em amount} and {\em quality} of the input examples (namely observations of plan executions generated by the aimed action model).

This paper addresses the learning of action models from a different source of knowledge, {\em deductive} knowledge, with the form of {\em state-invariants} (i.e logic formulae that specify constraints about the possible states of a given domain) to reduce the negative effects of insufficient input observations. Given an action model, state-of-the-art planners infer {\em state-invariants} from that model to reduce the planner search space and make the planning process more efficient~\cite{helmert2009concise}. In this paper we follow the opposite direction and leverage {\em state-invariants} to learn a planning action model.

Our approach extends the {\em classical planning} compilation for learning \strips\ action models~\cite{aineto2018learning}. Our extension is flexible to different kinds of input knowledge (e.g., partially/fully observations of actions of plan executions as well as partially/fully observed intermediate states) and outputs an action model that is {\em consistent} with the given input knowledge. The experimental results show that, at unfavorable scenarios where input observations are minimal (just an {\em initial state} and the {\em goals}), {\em state-invariant} help to learn better \strips\ models with the {\em classical planning} compilation.

@@

\subsection{State-invariants}
The notion of {\em state-constraint} is very general and has been used in different areas of AI and for different purposes.  If we restrict ourselves to planning, {\em state-constraints} are abstractions for compactly specifying sets of states. For instance, {\em state-constraints} in planning allow to specify the set of states where a given action is applicable, the set of states where a given {\em derived predicate} holds or the set of states that are considered goal states.

@@

\section{Learning \strips\ action models from {\em state-invariants}}
\label{sec:learning}
We define the task of learning an action model from {\em state-invariants} as a tuple $\Lambda=\tup{P,\Phi,M}$, where:
\begin{itemize}
\item $P=\tup{F,A[\cdot],I,G}$, is a {\em classical planning problem} where $A[\cdot]$ is a set of actions s.t., the semantics of each action $a\in A[\cdot]$ is {\em unknown} (i.e. the functions $\rho$ and/or $\theta$ are undefined for $a\in A[\cdot]$).
\item $\Phi$, a set of {\em state-invariants} that define constraints about the set of possible states.
\item $M$ is the {\em space of possible action models} for the $A[\cdot]$ actions (i.e., the set of possible specifications of the $\rho$ and/or $\theta$ functions for each action $a\in A[\cdot]$).
\end{itemize}

A {\em solution} to a $\Lambda=\tup{P,\Phi,M}$ learning task is a model $\mathcal{M}\in M$ such that there exists a plan $\pi$ that solves $P=\tup{F,A[\cdot],I,G}$, when the semantics of each action $a\in A[\cdot]$ is given by $\mathcal{M}$, and such that any state traversed by the trajectory $\tau(\pi,P)$ is {\em consistent} with the {\em state-invariants} in $\Phi$.

@@

Despite any element of ${\mathcal I}_{\Psi,\xi}$ can {\em a priori} appear in the $pre(\xi)$, $del(\xi)$ and $add(\xi)$ of schema $\xi$, the actual space of possible \strips\ schemata is bounded by constraints of three kinds:
\begin{enumerate}
\item {\bf Syntactic constraints}. \strips\ constraints require $del(\xi)\subseteq pre(\xi)$, $del(\xi)\cap add(\xi)=\emptyset$ and $pre(\xi)\cap add(\xi)=\emptyset$. Considering exclusively these syntactic constraints, the size of the space of possible \strips\ schemata is given by $2^{2\times|{\mathcal I}_{\Psi,\xi}|}$. {\em Typing constraints} are also of this kind~\cite{mcdermott1998pddl}. 
\item {\bf Domain-specific constraints}. One can introduce domain-specific knowledge to constrain further the space of possible schemata. For instance, in the {\em blocksworld} one can argue that {\small\tt on($v_1$,$v_1$)} and {\small\tt on($v_2$,$v_2$)} will not appear in the $pre(\xi)$, $del(\xi)$ and $add(\xi)$ lists of an action schema $\xi$ because, in this specific domain, a block cannot be on top of itself. {\it State invariants} are constraints of this kind. 
\item {\bf Observation constraints}. An observation $\mathcal{O}(\tau)$ depicts {\em semantic knowledge} that constraints further the space of possible action schemata.   
\end{enumerate}

@@

\subsection{Learning \strips\ action models with classical planning}
Given a $\Lambda=\tup{P,\Phi,M}$ learning task we create a classical planning problem $P_{\Lambda}=\tup{F_{\Lambda},A_{\Lambda},I,G_{\Lambda}}$ such that:
\begin{itemize}
\item $F_{\Lambda}$ extends $F$ with a fluent {\small$mode_{inval}$}, to indicate whether an action model is inconsistent with the input {\em state-invariants}, a fluent {\small$mode_{insert}$}, to indicate whether action models are being programmed, and the fluents for the propositional encoding of the corresponding space of STRIPS action models. This is a set of fluents of the type $\{pre\_e\_\xi, eff\_e\_\xi\}_{\forall e\in{\mathcal I}_{\Psi,\xi}}$ such that $e\in{\mathcal I}_{\Psi,\xi}$ is a single element from the set of FOL interpretations of predicates $\Psi$ over the corresponding action parameters $pars(\xi)$.

\item $G_{\Lambda}= G\cup \{\neg mode_{inval}\}$ extends the original goals $G$ with the $\neg mode_{inval}$ literal to validate that only states consistent with the state constraints in $\Phi$ are traversed.

\item $A_{\Lambda}$ replaces the actions in $A$ with two types of actions.
\begin{enumerate}
\item Actions for {\em inserting} a {\em precondition}, {\em positive} effect or {\em negative} effect in $\xi$ following the syntactic constraints of \strips\ models. In the particular case that $M$ is a {\em partially specified model} then only the actions for inserting a possible {\em precondition} or {\em effect} are necessary.
\begin{itemize}
\item Actions which support the addition of a {\em precondition} $p\in \Psi_{\xi}$ to the action model $\xi$. A precondition $p$ is inserted in $\xi$ when neither $pre_p$, $eff_p$ exist in $\xi$.

@@

\item Actions for {\em applying} an action model $\xi$ built by the {\em insert} actions and bounded to objects $\omega\subseteq\Omega^{|pars(\xi)|}$ (where $\Omega$ is the set of {\em objects} used to induce the fluents $F$ by assigning objects in $\Omega$ to the $\Psi$ predicates and $\Omega^k$ is the $k$-th Cartesian power of $\Omega$). The action parameters, $pars(\xi)$, are bound to the objects in $\omega$ that appear in the same position. These actions validate also that any state traversed by a solution plan is {\em consistent} with the {\em state-invariants} in $\Phi$.
\end{enumerate}
\end{itemize}

\begin{small}
\begin{align*}
\pre(\mathsf{apply_{\xi,\omega}})=&\{\neg mode_{inval}\},\\
\cond(\mathsf{apply_{\xi,\omega}})=&\{pre_{p}(\xi)\wedge eff_{p}(\xi)\}\rhd\{\neg p(\omega)\}_{\forall p\in\Psi_\xi},\\
&\{\neg pre_{p}(\xi)\wedge eff_{p}(\xi)\}\rhd\{p(\omega)\}_{\forall p\in\Psi\xi}\},\\
&\{pre_{p}(\xi)\wedge \neg p(\omega)\}\rhd\{mode_{inval}\}_{\forall p\in\Psi_\xi},\\
&\{\neg\phi\}\rhd\{mode_{inval}\}_{\forall \phi\in\Phi},\\
&\{\emptyset\}\rhd\{\neg mode_{insert}\},
\end{align*}
\end{small}

\subsection{Learning from partiallly specified models}
The compilation is defined assuming $M$ represents the {\em full} space of \strips\ action models, that is when learning action models from scratch. However, in some contexts it is reasonable to assume that some parts of the action model are known so there is no need to learn the entire model from scratch~\cite{ZhuoNK13}. Here we show that the compilations is also flexible to this particular learning scenario where $M$ is given by a {\em partially specified action model}, when some fragments of the aimed action model are a priori known, so $M$ represents a subspace of the of the possible \strips\ action models\cite{sreedharan2018handling}.

When the action model for a \strips\ schema $\xi$ is partially specified, the known preconditions and effects are encoded setting the corresponding fluents $\{pre\_e\_\xi, eff\_e\_\xi\}_{\forall e\in{\mathcal I}_{\Psi,\xi}}$ to true in the initial state. Further, the corresponding insert actions, $\mathsf{insertPre_{p,\xi}}$ and $\mathsf{insertEff_{p,\xi}}$, become unnecessary and are removed from $A_{\Lambda}$, thereby making the classical planning task $P_{\Lambda}$ easier to be solved.

For example, supose that the preconditions of the {\em blocksworld} action schema {\tt stack} are known, then the initial state $I$ is extended with litereals, {\small\tt(pre\_holding\_v1\_stack)} and {\small\tt(pre\_clear\_v2\_stack)} and the assocaited actions $\mathsf{insertPre_{holding_v1,stack}}$ and $\mathsf{insertPre_{clear_v2,stack}}$ can be safely removed from the $A_{\Lambda}$ action set without altering the {\em soundness} and {\em completeness} of the $P_{\Lambda}$ compilation.

\subsection{Compilation properties}
\begin{mylemma}
Soundness. Any classical plan $\pi_{\Lambda}$ that solves $P_{\Lambda}$ produces a \strips\ model $\mathcal{M}$ that solves the $\Lambda=\tup{P,\Phi,M}$ learning task.
\end{mylemma}

\begin{proof}[Proof]
\begin{small}
According to the $P_{\Lambda}$ compilation, once a given precondition or effect is inserted into the action model $\mathcal{M}$ it can never be removed back. In addition, once the action model $\mathcal{M}$ is applied it cannot be {\em reprogrammed}. In the compiled planning problem $P_{\Lambda}$, the value of the original fluents $F$ can exclusively be modified via $\mathsf{apply_{\xi,\omega}}$ actions.  Therefore, the set of goals $G$ can only be achieved executing an applicable sequence of $\mathsf{apply_{\xi,\omega}}$ actions that, starting in the corresponding initial state reach a state $G \subseteq s_n$ validating that every generated intermediate state is consistent with the input {\em state-invariants}. This is exactly the definition of a solution to the $\Lambda=\tup{P,\Phi,M}$ learning task. 
\end{small}
\end{proof}

\begin{mylemma}
Completeness. Any \strips\ model $\mathcal{M}$ that solves the $\Lambda=\tup{P,\Phi,M}$ learning task can be computed with a classical plan $\pi_{\Lambda}$ that solves $P_{\Lambda}$.
\end{mylemma}

\begin{proof}[Proof]
\begin{small}
By definition ${\mathcal I}_{\Psi,\xi}$ fully captures the set of elements that can appear in a \strips\ action schema $\xi$ using predicates $\Psi$. In addition the $P_{\Lambda}$ compilation does not discard any possible action model $\mathcal{M}$ definable within ${\mathcal I}_{\Psi,\xi}$. This means that for every \strips\ model $\mathcal{M}$ that solves the $\Lambda=\tup{P,\Phi,M}$, we can build a plan $\pi_{\Lambda}$ that solves $P_{\Lambda}$ by selecting the appropriate actions for inserting precondition and effects to the corresponding action model $\mathcal{M}$ and then, selecting the corresponding $\mathsf{apply_{\xi,\omega}}$ actions that transform the initial state $I$ into a state that satisfies the goals $G$.
\end{small}
\end{proof}

The size of the classical planning task $P_{\Lambda}$ output by our compilation depends on the arity of the given {\em predicates} $\Psi$, that shape the propositional state variables $F$, and the number of parameters of the action models, $|pars(\xi)|$. The larger these arities, the larger $|{\mathcal I}_{\Psi,\xi}|$. The size of the ${\mathcal I}_{\Psi,\xi}$ set is the term that dominates the compilation size because it defines the $pre_p(\xi)/del_p(\xi)/add_p(\xi)$ fluents, the corresponding set of {\em insert} actions, and the number of conditional effects in the $\mathsf{apply_{\xi,\omega}}$ actions.

Note that {\em typing} can be used straightforward to constrain the FOL interpretations of $\Psi$ over the parameters $pars(\xi)$ which significantly reduces $|{\mathcal I}_{\Psi,\xi}|$ and hence, the size of the classical planning task output by the compilation.

\section{Learning from observations of plan executions}
\label{sec:observations}
So far we have explained the compilation for learning from a single input trace. However, the compilation is extensible to the more general case $\Lambda=\tup{\mathcal{M},\mathcal{T}}$, where $\mathcal{T}=\{\tau_1,\ldots,\tau_k\}$ is a set of plan traces. Taking this into account, a small modification is required in our compilation approach. In particular, the actions in $P_{\Lambda}$ for {\em validating} the last state $s_m^t\in \tau_t$, {\tt\small $1\leq t\leq k$} of a plan trace $\tau_t$ reset the current state and the current plan. These actions are now redefined as:

Inductive approaches for the learning planning action models compute an action model that maximizes some notion of {\em statistical consistency} over a set of observations of plan executions so output an action model in our case a solution to the addressed learning task is an action model that is {\em consistent} with the input knowledge.

@@

\subsection{Learning from observations with {\em classical planning}}
The work on {\em plan recognition as planning} usually assumes an observation model that is referred only to logs of executed actions. However, the approach applies also to more expressive observation models that consider state observations as well, like the observation model defined above, with a simple three-fold extension:
\begin{itemize}
\item One fluent $\{validated_j\}_{0\leq j\leq m}$ to point at every $s_j^o\in\mathcal{O}(\tau)$ state observation. Two fluents, $at_i$ and $next_{i,i+1}$, {\small $1\leq i \leq n$}, to iterate through the $n$ observed actions of $\tau$. The former is used to ensure that actions are executed in the same order as they are observed in $\tau$. The latter is used to iterate to the next planning step when solving $P_{\Lambda}$.
\item Adding $at_1$ and $\{next_{i,i+1}\}$, {\small $1\leq i \leq n$} to the initial state and $validated_m$ to every possible goal $G\in G[\cdot]$ to constrain solution plans $\pi^\top$ to be consistent with all the state observations.
